### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Improved upon visualization caption.

\begin{figure}[htb]
\begin{center}
	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
	\caption{WARP execution time with floating point-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations. Values outside of their respective standard deviations are not presented for the sake of clarity.}
	\label{fig:contribution:results:warp:msswarp}
\end{center}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
	\resizebox{ \columnwidth }{!}{\input{../msswarp}}
	\caption{Execution time using WARP with floating point-precision for the Basic- and Tiled kernels, indicated by their respective mean- and seperated by standard deviation values. Samples outside of respective standard deviation are not presented.}
	\label{fig:contribution:results:warp:msswarp}
\end{center}
\end{figure}
